---
title: "RWorksheet_Arenal#1"
author: "Jo Carlo Arenal"
date: "2024-09-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

# 1
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)

length(age)

# 2
fractions <- 1 / age
fractions

# 3
new_age <- c(age, 0, age)
new_age

# 4
sorted_age <- sort(age)
sorted_age

# 5
min_age <- min(age)
max_age <- max(age)
min_age
max_age

# 6
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)

length(data)

# 7

doubled_data <- 2 * data
doubled_data

#8
# 8.1 
seq_1_to_100 <- seq(1, 100)
seq_1_to_100

# 8.2
seq_20_to_60 <- seq(20, 60)
seq_20_to_60

# 8.3
mean_20_to_60 <- mean(seq_20_to_60)
mean_20_to_60

# 8.4
sum_51_to_91 <- sum(seq(51, 91))
sum_51_to_91

# 8.5
seq_1_to_1000 <- seq(1, 1000)
seq_1_to_1000

max_10_in_seq_1_to_1000 <- seq_1_to_1000[1:10]
max_10_in_seq_1_to_1000

# 9
filtered_vector <- Filter(function(i) { all(i %% c(3,5,7) !=0)}, seq(100))
filtered_vector

# 10
reverse_seq <- rev(seq(1,100))
reverse_seq

# 11
numbers_below_25 <-(seq(1,24))
numbers_below_25                    
                    
natural_numbers_below_25 <-Filter(function(i) {all(i%% c(3,5)!=0)},seq(25))
natural_numbers_below_25

#12 x <- {0 + x + 5 + }
#When you run this code, R will return an error because it cannot interpret or
# complete the expression because of the dangling + sign

#13

score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)

score_2 <- score[2]
score_3 <- score[3]

score_2
score_3

#14

a <- c(1, 2, NA, 4, NA, 6, 7)

print(a, na.print="-999")

#15

name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is", name, "and I am", age, "years old."))
print(R.version.string)







